---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align="center"
)
library(rjd3tramoseats)
```

# rjd3tramoseats

rjd3tramoseats offers full acces to options and outputs of TRAMO-SEATS (`rjd3tramoseats::tramoseats()`), including TRAMO modelling (`rjd3tramoseats::tramo()`) and SEATS decomposition (`rjd3tramoseats::seats_decompose()`).

The specification can be created with the functions `rjd3tramoseats::spec_tramo()` or `rjd3tramoseats::spec_tramoseats()` and can be modified with the function:

- for the pre-processing: `rjd3toolkit::set_arima()`, `rjd3toolkit::set_automodel()`, `rjd3toolkit::set_basic()`, `rjd3toolkit::set_easter()`, `rjd3toolkit::set_estimate()`, `rjd3toolkit::set_outlier()`, `rjd3toolkit::set_tradingdays()`, `rjd3toolkit::set_transform()`, `rjd3toolkit::add_outlier()`, `rjd3toolkit::remove_outlier()`, `rjd3toolkit::add_ramp()`, `rjd3toolkit::remove_ramp()`, `rjd3toolkit::add_usrdefvar()`;

- for the decomposition: `rjd3tramoseats::set_seats()`;

- for the benchmarking: `rjd3toolkit::set_benchmarking()`.
 

## Installation


```{r, eval = FALSE}
# Install development version from GitHub
# install.packages("remotes")
remotes::install_github("rjdemetra/rjd3toolkit")
remotes::install_github("rjdemetra/rjd3tramoseats")
```

## Usage

```{r ts-final}
library(rjd3tramoseats)
y <- rjd3toolkit::ABS$X0.2.09.10.M
ts_model <- tramoseats(y) 
summary(ts_model$result$preprocessing) # Summary of tramo model
plot(ts_model) # Plot of the final decomposition
```

To get the final components you can use the function `rjd3toolkit::sa_decomposition()`:

```{r ts-fin-comp}
rjd3toolkit::sa_decomposition(ts_model)
```
